---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HCVisR

<!-- badges: start -->
<!-- badges: end -->

## Overview

`HCVisR` is an interactive R Shiny app package that provides a comprehensive tool for generating, visualizing, and analyzing time series data within the Entropy-Statistical Complexity (H × C) framework. Based on the methodology of Bandt and Pompe (2002), this app enables users to explore the entropy and complexity characteristics of various types of time series, both stochastic and deterministic, by mapping them onto the H × C plane. 

## Key Features

- **Time Series Generation**: `HCVisR` supports the generation of multiple types of time series, including stochastic (e.g., White Noise, AR, ARMA) and deterministic (e.g., Logistic Map, Henon Map) models.

- **H × C Plane Visualization**: The app calculates normalized Shannon entropy (H) and statistical complexity (C) for each time series using ordinal patterns. This calculation relies on the [StatOrdPattHxC](https://github.com/arey1911/StatOrdPattHxC) package, which provides the necessary functions for ordinal pattern analysis and entropy-complexity mapping. Each time series is visualized as a data point on the H × C plane, enabling users to identify patterns and gain insights into the behavior of different time series types.

- **Mixing Time Series**: `HCVisR` provides a unique feature for "mixing" two time series through addition or multiplication. Users can select two generated time series and apply these operations, creating a new combined series. The app dynamically updates the H × C visualization, showing how the combination affects entropy and complexity.

## Installation

You can install the development version of `HCVisR` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alexkzw/HCVisR")
```

## Launching the R Shiny app

The R Shiny app can be launched with:

```{r, eval=F, warning=F, message=F}
library(HCVisR)
HCVisR::launchApp()
```


## Vignette

A vignette is available here: https://github.com/alexkzw/HCVisR/blob/master/vignettes/HCVisR-vignette.pdf

## Reference

1. C. Bandt and B. Pompe. Permutation entropy: A natural complexity measure for time series. Physical Review Letters, 88:174102–1–174102–4, 2002. doi: 10.1103/PhysRevLett.88.174102.

2. https://github.com/arey1911/StatOrdPattHxC
