---
title: "HCVisR: Time Series Generation and H x C Visualisation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HCVisR: Time Series Generation and H x C Visualisation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

`HCVisR` is a Shiny-based R package for generating time series and visualising them on the H x C (Entropy and Complexity) plane. This package allows users to generate both stochastic and deterministic time series and perform basic operations like addition and multiplication on selected time series.

# Installation

You can install the development version from GitHub:

```{r}
# install.packages("remotes")
#remotes::install_github("alexkzw/HCVisR")
```

# Basic Usage

To start the Shiny app, use the following command:

```{r}
library(HCVisR)
#HCVisR::app_ui()
```

The app provides options for generating and uploading time series. Users can visualise the time series and see its position on the H x C plane based on the selected embedding dimension.

# Example

Here’s an example of how to generate a stochastic AR(1) time series and visualise it:
```{r}
# Generate AR(1) Time Series
ts_ar <- new_stochastic_ts("AR", n = 200, phi = 0.5)

# Print and visualize the series
print(ts_ar)
plot(ts_ar)
```

