---
title: "HCVisR: Time Series Generation and H x C Visualisation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HCVisR: Time Series Generation and H x C Visualisation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

The `HCVisR` package provides an interactive Shiny app for generating and visualizing time series data in the H × C plane. The app supports stochastic and deterministic time series generation, allows "mixing" two time series with addition or multiplication, and visualizes points in the H × C plane using Shannon Entropy (H) and Statistical Complexity (C), relying on the StatOrdPattHxC package for ordinal pattern analysis.

# Introduction to the H x C Plane

The H × C plane, representing Shannon Entropy (H) and Statistical Complexity (C), provides a way to understand the structure and predictability of time series. **Shannon Entropy (H)** measures the randomness in the series, while **Statistical Complexity (C)** assesses the complexity or structural richness. Together, they allow for an insightful visualization of different types of time series.

# Installation

You can install the development version from GitHub:

```{r}
#install.packages("remotes") 
#remotes::install_github("alexkzw/HCVisR")
library(HCVisR)
```

# Basic Usage

To start the Shiny app, use the following command:

```{r, warning=F, message=F, eval=F}
HCVisR::launchApp()
```

The app provides options for generating and uploading time series. Users can visualise the time series and see its position on the H x C plane based on the selected embedding dimension.

# Using the Shiny App Interface

The app interface contains several main sections:

- **Time Series Generation**: Generate stochastic or deterministic time series by specifying parameters.

- **File Upload**: Upload your time series in CSV format (one column, numeric values only, and maximum of 1000 data points).

- **Embedding Dimension Selection**: Choose an embedding dimension (3 to 6) for H and C calculations.

- **Plot Visualizations**: View the time series plot and its corresponding H x C point based on selected parameters.

# Example Workflow

Here’s an example of how to generate a stochastic AR(1) time series and visualise it:
```{r fig.width=7, warning=F, message=F}
# Generate AR(1) Time Series
ts_ar <- new_stochastic_ts("AR", n = 300, phi = 0.5)

# Print the time series
print(ts_ar)

# Visualise the time series
plot(ts_ar)

# Get a summary of the series
summary(ts_ar)
```

User can also generate a deterministic time series and explore it with the same object-oriented methods:
```{r fig.width=7, warning=F, message=F}
# Generate logistic time series
ts_logistic <- new_deterministic_ts(model = "logistic", N = 300)

# Print the time series
print(ts_logistic)

# Visualise the time series
plot(ts_logistic)

# Get a summary of the series
summary(ts_logistic)
```

Users can then combine two time series via addition or multiplication. Below is an example of combining the previously generated AR(1) and the logistic time series:

```{r fig.width=7, warning=F, message=F}
# Combine AR(1) and White Noise time series using addition
combined_add <- combine.TimeSeries(ts_ar, ts_logistic, method = "add", alpha = 0.5)

# Print the combined series
print(combined_add)

# Visualize the combined series
plot(combined_add)

# Get a summary of the combined series
summary(combined_add)
```

You can also combine them using multiplication:
```{r fig.width=7, warning=F, message=F}
# Combine AR(1) and White Noise time series using multiplication
combined_multiply <- combine.TimeSeries(ts_ar, ts_logistic, method = "multiply")

# Print the combined series
print(combined_multiply)

# Visualize the combined series
plot(combined_multiply)

# Get a summary of the combined series
summary(combined_multiply)
```

# Exploring Embedding Dimensions

The embedding dimension affects the calculation of H and C. Users can select an embedding dimension (3 to 6) in the app to explore different structural views. Higher dimensions provide a richer view of complexity, though with increased computation.

# Viewing the H x C plot

To view the H × C visualization:

1. Select a time series or upload your data.
2. Choose the desired embedding dimension (3-6).
3. The plot will display the computed entropy-complexity point in the H x C plane.

This tool is valuable for examining how different types of time series—stochastic or deterministic—position themselves within the entropy-complexity landscape.

# Additional Resources and References

- For more on entropy and complexity calculations, refer to the [StatOrdPattHxC](https://github.com/arey1911/StatOrdPattHxC) package.

- Read more about the application of the H × C plane in the context of time series in the [Bandt and Pompe (2002)](https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.88.174102) paper.
