---
title: "HCVisR: Time Series Generation and H x C Visualisation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HCVisR: Time Series Generation and H x C Visualisation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

`HCVisR` is a Shiny-based R package for generating time series and visualising them on the H x C (Entropy and Complexity) plane. This package allows users to generate both stochastic and deterministic time series and perform basic operations like addition and multiplication on selected time series.

# Installation

You can install the development version from GitHub:

```{r, eval = FALSE}
# install.packages("remotes")
#remotes::install_github("alexkzw/HCVisR")
```

# Basic Usage

To start the Shiny app, use the following command:

```{r}
library(HCVisR)
#HCVisR::app_ui()
```

The app provides options for generating and uploading time series. Users can visualise the time series and see its position on the H x C plane based on the selected embedding dimension.

# Example

Here’s an example of how to generate a stochastic AR(1) time series and visualise it:
```{r fig.width=7}
# Generate AR(1) Time Series
ts_ar <- new_stochastic_ts("AR", n = 200, phi = 0.5)

# Print the time series
print(ts_ar)

# Visualise the time series
plot(ts_ar)

# Get a summary of the series
summary(ts_ar)
```

User can generate another stochastic time series and explore it with the same object-oriented methods:
```{r fig.width=7}
# Generate White Noise Time Series
ts_wn <- new_stochastic_ts("WN", n = 200)

# Print the time series
print(ts_wn)

# Visualise the time series
plot(ts_wn)

# Get a summary of the series
summary(ts_wn)
```

Users can then combine two time series via addition or multiplication. Below is an example of combining the previously generated AR(1) and the white noise time series:

```{r fig.width=7}
# Combine AR(1) and White Noise time series using addition
combined_add <- combine.TimeSeries(ts_ar, ts_wn, method = "add", alpha = 0.5)

# Print the combined series
print(combined_add)

# Visualize the combined series
plot(combined_add)

# Get a summary of the combined series
summary(combined_add)
```

You can also combine them using multiplication:
```{r fig.width=7}
# Combine AR(1) and White Noise time series using multiplication
combined_multiply <- combine.TimeSeries(ts_ar, ts_wn, method = "multiply", alpha = 0.5)

# Print the combined series
print(combined_multiply)

# Visualize the combined series
plot(combined_multiply)

# Get a summary of the combined series
summary(combined_multiply)
```

